
\centerline{\textbf{ \LARGE Synchronization}}


% ----------------------------------------------------------------------------


\begin{enumerate}

  \item Critical Section is part of a program where a process manipulates shared variables.
  \item Correct Solution
  \begin{enumerate}
    \item Mutual exclusion : no 2 processes can be in critical sections simultaneously.
    \item Progress : only competing processes are considered for decision as to who goes next.
    \item Bounded wait :
  \end{enumerate}


  \item Turn Variable:
  \begin{enumerate}
    \item Only for 2 process.
    \item strict alternation.
    \ item shared variable - turn
    \item while( not\_my\_turn ) do-nothing;
  \end{enumerate}
      \begin{myTableStyle}
        \begin{tabular}{ |m{5cm}|m{5cm}| } \hline
            \lstinputlisting[language=Octave]{./code/turnVariable_01.c}   &     \lstinputlisting[language=Octave]{./code/turnVariable_02.c}   \\ \hline
        \end{tabular}
      \end{myTableStyle}
      \vspace{0.08in}

  \item Peterson's Solution:
  \begin{enumerate}
    \item Only for 2 process.
    \item No alternation.
    \item shared variable - turn, flag
    \item while( not\_my\_turn and other\_wants\_to\_go ) do-nothing;
  \end{enumerate}
      \begin{myTableStyle}
        \begin{tabular}{ |m{6cm}|m{6cm}| } \hline
            \lstinputlisting[language=Octave]{./code/peterson_01.c}   &   \lstinputlisting[language=Octave]{./code/peterson_02.c}   \\ \hline
        \end{tabular}
      \end{myTableStyle}
      \vspace{0.08in}

 \begin{minipage}{\linewidth}
  \item Binary Semaphore : work for many process. \\
      \begin{myTableStyle}
        \begin{tabular}{ |m{4.5cm}|m{5cm}|m{3.5cm}| } \hline
            \lstinputlisting[language=Octave]{./code/semaphore_01_wait.c}   &
            \lstinputlisting[language=Octave]{./code/semaphore_01_signal.c} &
            \lstinputlisting[language=Octave]{./code/semaphore_01.c} \\ \hline
        \end{tabular}
      \end{myTableStyle}
      \vspace{0.08in}
  \begin{enumerate}
    \item Value of S can be 0 or 1.
    \item if( s == 1 ) then no   process is in CS
    \item if( s == 0 ) then one process is in CS
    \item Drawback :
    \begin{enumerate}
      \item Busy waiting, wasting cpu cycles because of the while loop.
      \item Priority inversion.
  \end{enumerate}
  \item Counting semaphore
  \begin{enumerate}
    \item Can take values other than 0, 1.
    \item if( s=5 ) then 5 processes can enter CS.
  \end{enumerate}
  \end{enumerate}
  \end{minipage}
  \vspace{0.08in}

  \item Reader Writer Problem
  \begin{enumerate}
    \item Two semaphore are needed
      \begin{enumerate}
        \item wrt : for resource access
        \item mutex: for access to readCount variable.
      \end{enumerate}
    \item First reader will wait for the writer to exit. Last reader will signal the writer.
  \end{enumerate}




\end{enumerate}

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------
