\centerline{\textbf{ \LARGE Memory Access Time Numericals}}



% ----------------------------------------------------------------------------

\begin{questyle}

  \question  In a two-level virtual memory, the memory access time for main memory,   {\large \(  t_{M}=10^{-8}  \) }  sec, and the memory access time for
            the secondary memory,  {\large \( t_D=10^{-3} \) }  sec. What must be the hit ratio, H such that the access efficiency is within 80 percent
            of its maximum value?(GATE-1990)

\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question  If an instruction takes i microseconds and a page fault takes an additional j microseconds, the effective
              instruction time if on the average a  page fault occurs every k instructions is: (GATE-1998)

  \begin{choices}
    \choice {\large \( \mathbf { i + j/k } \) }
    \choice {\large \( \mathbf { i + j* k } \) }
    \choice {\large \( \mathbf { (i + j)/ k } \) }
    \choice {\large \( \mathbf { (i + j)* k } \) }
  \end{choices}

\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question  Suppose the time to service a page fault is on the average 10 milliseconds, while a memory access takes 1 microsecond.
             Then a 99.99\% hit ratio results in average memory access time of (GATE-2000)

  \begin{choices}
    \choice 1.9999 milliseconds
    \choice 1 millisecond
    \choice 9.999 microseconds
    \choice 1.9999 microseconds
  \end{choices}

\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question  A processor uses 2-level page tables for virtual to physical address translation. Page tables for
             both levels are stored in the main memory. Virtual and physical addresses are both 32 bits wide.
             The memory is byte addressable. For virtual to physical address translation, the 10 most significant
             bits of the virtual address are used as index into the first level page table while the next 10 bits
             are used as index into the second level page table. The 12 least significant bits of the virtual
             address are used as offset within the page. Assume that the page table entries in both levels of
             page tables are 4 bytes wide. Further, the processor has a translation look-aside buffer (TLB), with a
             hit rate of 96\%. The TLB caches recently used virtual page numbers and the corresponding physical
             page numbers. The processor also has a physically addressed cache with a hit rate of 90\%.
             Main memory access time is 10 ns, cache access time is 1 ns, and TLB access time is also 1 ns.

            Assuming that no page faults occur, the average time taken to access a virtual address is
            approximately (to the nearest 0.5 ns) (GATE-2003)

            \begin{choices}
              \choice 1.5 ns
              \choice 2 ns
              \choice 3 ns
              \choice 4 ns
            \end{choices}

\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question  Consider a system with a two-level paging scheme in which a regular memory access takes 150
             nanoseconds, and servicing a page fault takes 8 milliseconds. An average instruction takes
             100 nanoseconds of CPU time, and two memory accesses. The TLB hit ratio is 90\%, and the
             page fault rate is one in every 10,000 instructions. What is the effective average
             instruction execution time? (GATE-2004)

  \begin{choices}
    \choice 645 nanoseconds
    \choice 1050 nanoseconds
    \choice 1215 nanoseconds
    \choice 1230 nanoseconds
  \end{choices}

\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question Let the page fault service time be 10ms in a computer with average memory access time being 20ns.
            If one page fault is generated for every {\large \(10^6\) }  memory accesses, what is the effective access time
            for the memory? (GATE-2011)

  \begin{choices}
    \choice 21ns
    \choice 30ns
    \choice 23ns
    \choice 35ns
  \end{choices}

\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question  Consider a paging hardware with a TLB. Assume that the entire page table and all the pages
            are in the physical memory. It takes 10 milliseconds to search the TLB and 80 milliseconds to
            access the physical memory. If the TLB hit ratio is 0.6, the effective memory access
            time (in milliseconds) is \fillin[] (GATE-2014\_set\_3)

\end{questyle}


% ----------------------------------------------------------------------------


% ----------------------------------------------------------------------------


% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------


% ----------------------------------------------------------------------------


% ----------------------------------------------------------------------------


% ----------------------------------------------------------------------------


% ----------------------------------------------------------------------------


% ----------------------------------------------------------------------------



% ----------------------------------------------------------------------------


% ----------------------------------------------------------------------------


% ----------------------------------------------------------------------------



% ----------------------------------------------------------------------------


% ----------------------------------------------------------------------------


% ----------------------------------------------------------------------------



% ----------------------------------------------------------------------------


% ----------------------------------------------------------------------------


% ----------------------------------------------------------------------------
