
\centerline{\textbf{ \LARGE Paging}}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question  In a paged segmented scheme of memory management, the segment table itself must have
             a page table because (GATE-1995)

  \begin{choices}
    \correctchoice The segment table is often too large to fit in one page
    \choice Each segment is spread over a number of pages
    \choice Segment tables point to page tables and not to the physical locations of the segment
    \choice The processor’s description base register points to a page table
  \end{choices}
\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question Dirty bit for a page in a page table. (GATE-1997)

  \begin{choices}
    \correctchoice helps avoid unnecessary writes on a paging device
    \choice helps maintain LRU information
    \choice allows only read on a page
    \choice none of the above
  \end{choices}
\end{questyle}


% ----------------------------------------------------------------------------

\begin{questyle}

  \question In a system with 32 bit virtual addresses and 1 KB page size, use of one-level page tables for virtual to
            physical address translation is not practical because of. (GATE-2003)

  \begin{choices}
    \choice the large amount of internal fragmentation
    \choice the large amount of external fragmentation
    \correctchoice the large memory overhead in maintaining page tables
    \choice  the large computation overhead in the translation process
  \end{choices}

\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question  The minimum number of page frames that must be allocated to a running process in a virtual memory
            environment is determined by(GATE-2004)

  \begin{choices}
    \correctchoice the instruction set architecture
    \choice page size
    \choice number of processes in memory
    \choice physical memory size
  \end{choices}

\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question  The essential content(s) in each entry of a page table is / are (GATE-2009)

  \begin{choices}
    \choice Virtual page number
    \correctchoice Page frame number
    \choice Both virtual page number and page frame number
    \choice Access right information
  \end{choices}

\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question  Consider a system with byte-addressable memory, 32 bit logical addresses, 4 kilobyte page size and page table entries of 4 bytes each. The size of the page table in the system is \fillin[4 MB] (GATE-2015\_set\_1)

\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question  Under paged memory management scheme, simple lock and key memory protection arrangement may still be required if the \fillin[] processors do not have address mapping hardware. (GATE-1990)

\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question  Consider a machine with 64 MB physical memory and a 32-bit virtual address space. If the page size is 4KB, what
              is the approximate size of the page table?(GATE-2001)

  \begin{choices}
    \choice 16 MB
    \choice 8 MB
    \correctchoice 2 MB
    \choice 24 MB
  \end{choices}

\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question  A processor uses 2-level page tables for virtual to physical address translation. Page tables for
             both levels are stored in the main memory. Virtual and physical addresses are both 32 bits wide.
             The memory is byte addressable. For virtual to physical address translation, the 10 most significant
             bits of the virtual address are used as index into the first level page table while the next 10 bits
             are used as index into the second level page table. The 12 least significant bits of the virtual
             address are used as offset within the page. Assume that the page table entries in both levels of
             page tables are 4 bytes wide.
             Suppose a process has only the following pages in its virtual address space: two contiguous code
             pages starting at virtual address 0x00000000, two contiguous data pages starting at virtual
             address 0×00400000, and a stack page starting at virtual address 0×FFFFF000. The amount of memory
             required for storing the page tables of this process is: (GATE-2003)

            \begin{choices}
              \choice 8 KB
              \choice 12 KB
              \correctchoice 16 KB
              \choice 20 KB
            \end{choices}

\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question  A processor uses 36 bit physical addresses and 32 bit virtual addresses, with a page frame size
             of 4 Kbytes. Each page table entry is of size 4 bytes. A three level page table is used for virtual to
             physical address translation, where the virtual address is used as follows (GATE-2008)
            \begin{enumerate}
                \item[*] Bits 30-31 are used to index into the first level page table
                \item[*] Bits 21-29 are used to index into the second level page table
                \item[*] Bits 12-20 are used to index into the third level page table, and
                \item[*] Bits 0-11 are used as offset within the page
            \end{enumerate}
            The number of bits required for addressing the next level page table (or page frame) in the page table entry of the first, second and third level page tables are respectively. https://www.cs.utexas.edu/~lorenzo/corsi/cs372/06F/hw/3sol.html

  \begin{choices}
    \choice 20, 20 and 20
    \choice 24, 24 and 24
    \choice 24, 24 and 20
    \correctchoice 25, 25 and 24
  \end{choices}

\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question  A multilevel page table is preferred in comparison to a single level page table for translating virtual
             address to physical address because (GATE-2009)

  \begin{choices}
    \choice It reduces the memory access time to read or write a memory location.
    \correctchoice It helps to reduce the size of page table needed to implement the virtual address space of a process
    \choice It is required by the translation lookaside buffer.
    \choice It helps to reduce the number of page faults in page replacement algorithms.
  \end{choices}

\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question  A computer uses 46–bit virtual address, 32–bit physical address, and a three–level paged page table organization.
             The page table base register stores the base address of the first–level table (T1), which occupies
             exactly one page. Each entry of T1 stores the base address of a page of the second–level table (T2).
             Each entry of T2 stores the base address of a page of the third–level table (T3). Each entry of T3
             stores a page table entry (PTE). The PTE is 32 bits in size. The processor used in the computer has
             a 1 MB 16 way set associative virtually indexed physically tagged cache. The cache block size
             is 64 bytes. What is the size of a page in KB in this computer? (GATE-2013)

  \begin{choices}
    \choice 2
    \choice 4
    \correctchoice 8
    \choice 16
  \end{choices}

\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question   A Computer system implements 8 kilobyte pages and a 32-bit physical address space. Each page table
              entry contains a valid bit, a dirty bit three permission bits, and the translation. If the maximum size
              of the page table of a process is 24 megabytes, the length of the virtual address
              supported by the system is \fillin[36] (GATE-2015\_set\_2)
\end{questyle}

% ----------------------------------------------------------------------------

\begin{questyle}

  \question  Consider a computer system with 40-bit virtual addressing and page size of sixteen kilobytes.
              If the computer system has a one-level page table per process and each page table entry requires 48 bits,
              then the size of the per-process page table is\fillin[384] megabytes. (GATE-2016\_set\_1)

\end{questyle}

% ----------------------------------------------------------------------------
Note : old gate written questions of 5 mark  are left and not yet included in this library. Till 2002. \\
Note : File system and device management questions are left.
% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------
