\centerline{\textbf{ \LARGE Deadlock : Bankers Algorith}}

% ----------------------------------------------------------------------------
\begin{questyle}

  \question  A single processor system has three resource types X, Y and Z, which are shared by three processes.
             There are 5 units of each resource type. Consider the following scenario, where the column alloc denotes the number
             of units of each resource type allocated to each process, and the column request denotes the number of units of
             each resource type requested by a process in order to complete execution. Which of these processes will finish LAST?(GATE-2007)

        \begin{lstlisting}
                alloc           request
                X Y Z            X Y Z
            P0  1 2 1            1 0 3
            P1  2 0 1            0 1 2
            P2  2 2 1            1 2 0
        \end{lstlisting}

  \begin{oneparchoices}
    \choice P0
    \choice P1
    \choice P2
    \choice system is in deadlock
  \end{oneparchoices}

  \end{questyle}


% ----------------------------------------------------------------------------

\begin{questyle}

  \question  An operating system uses the Banker’s algorithm for deadlock avoidance when managing the allocation of
             three resource types X, Y, and Z to three processes P0, P1, and P2. The table given below presents the
             current system state. Here, the Allocation matrix shows the current number of resources of each type
             allocated to each process and the Max matrix shows the maximum number of resources of each type required
             by each process during its execution. (GATE-2014\_set\_1)

             \begin{lstlisting}
                alloc           request
                X Y Z            X Y Z
            P0  0 0 1            8 4 3
            P1  3 2 0            6 2 0
            P2  2 2 1            3 3 3
            \end{lstlisting}


             There are 3 units of type X, 2 units of type Y and 2 units of type Z still available. The system is
             currently in a safe state. Consider the following independent requests for additional resources in the current state:

             REQ1: P0 requests 0 units of X, 0 units of Y and 2 units of Z \\
             REQ2: P1 requests 2 units of X, 0 units of Y and 0 units of Z \\
             Which one of the following is TRUE?
  \begin{choices}
    \choice  Only REQ1 can be permitted.
    \choice  Only REQ2 can be permitted.
    \choice  Both REQ1 and REQ2 can be permitted.
    \choice  Neither REQ1 nor REQ2 can be permitted
  \end{choices}

  \end{questyle}



% ----------------------------------------------------------------------------

\begin{questyle}

  \question   A system shares 9 tape drives. The current allocation and maximum requirement of tape drives for 3 processes are shown below:(GATE-2017\_set\_2)

  \begin{lstlisting}
                alloc   Max
            P1   3      7
            P2   1      6
            P3   3      5
            \end{lstlisting}

  Which of the following best describes the current state of the system?
  \begin{choices}
    \choice Safe, Deadlocked
    \choice Safe, Not Deadlocked
    \choice Not Safe, Deadlocked
    \choice Not Safe, Not Deadlocked
  \end{choices}

  \end{questyle}



% ----------------------------------------------------------------------------
old gate written questions of 5 mark  are left and not yet included in this library. Till 2002.
% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

