\centerline{\textbf{ \LARGE Threads}}


% ----------------------------------------------------------------------------

\begin{questyle}

  \question  Threads of a process share (GATE - 2017\_set\_1)

  \begin{choices}
    \choice Global variable but not heap.
    \choice Heap but not global variable.
    \choice Neither global variable nor heap.
    \CorrectChoice Both heap and global variables
  \end{choices}


  \end{questyle}



% ----------------------------------------------------------------------------


\begin{questyle}

  \question  Which of the following is/are shared by all the threads in a process? (GATE - 2017\_set\_2)
    \begin{oneparchoices}
      \choice Program counter
      \choice Stack
      \CorrectChoice Address Space
      \choice Registers
    \end{oneparchoices}


  \end{questyle}



% ----------------------------------------------------------------------------


\begin{questyle}

  \question Consider the following statements with respect to user-level threads and
            kernel supported threads. Which of the statements are true?(GATE - 2004 )

    \begin{enumerate}
      \item[i] Context switching is faster in kernel threads.
      \item[ii] System call blocks all user threads.
      \item[iii] Kernel threads can be scheduled independently.
      \item[iv] User threads are transparent to kernel.
    \end{enumerate}

  \begin{oneparchoices}
    \CorrectChoice (ii), (iii) and (iv) only
    \choice (ii) and (iii) only
    \choice (i) and (iii) only
    \choice (i) and (ii) only
  \end{oneparchoices}


  \end{questyle}



% ----------------------------------------------------------------------------


\begin{questyle}

  \question Consider the following statements about user level threads and kernel level threads.
            Which one of the following statement is FALSE? (GATE -  2007)

  \begin{choices}
    \choice Kernel threads have more context switch time.
    \choice User threads need no hardware support.
    \choice Related kernal threads can be scheduled on different processors.
    \CorrectChoice Blocking one kernal threads block all related threads.
  \end{choices}


  \end{questyle}



% ----------------------------------------------------------------------------


\begin{questyle}

  \question  A thread is usually defined as a “light weight process” because an operating system (OS)
            maintains smaller data structures for a thread than for a process. In relation to this, which
            of the following is TRUE? (GATE - 2011)

  \begin{choices}
    \choice On per-thread basis, the OS maintains only CPU register state
    \choice The OS does not maintain a separate stack for each thread
    \CorrectChoice On per-thread basis, the OS does not maintain virtual memory state
    \choice On per-thread basis, the OS maintains only scheduling and accounting information.
  \end{choices}


  \end{questyle}



% ----------------------------------------------------------------------------


\begin{questyle}

  \question  Choose the false option. (GATE - 2014\_set\_1)

  \begin{choices}
    \choice User level threads are not scheduled by kernel.
    \choice Blocking one user thread will block all threads of the process.
    \choice User threads have less context switching compared to kernel threds.
    \CorrectChoice Kernel threads can not share the code segment.
  \end{choices}


  \end{questyle}

% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
