
\centerline{\textbf{ \LARGE Scheduling Algorithms}}


\setcounter{question}{0}

% ----------------------------------------------------------------------------

\begin{minipage}{\linewidth}

\question Which policy is best for time sharing OS. (GATE - 95)

\begin{oneparchoices}
   \choice SJF
   \choice Round Robin
   \choice FCFS
   \choice SRTF
\end{oneparchoices}

\end{minipage}

% ----------------------------------------------------------------------------

\begin{minipage}{\linewidth}


\question State transition diagram represents . (GATE - 96)
\begin{choices}
   \choice Batch OS
   \choice OS with preemptive scheduling
   \choice OS with non-preemptive scheduling
   \choice Uni-programmed OS
\end{choices}


\end{minipage}

% ----------------------------------------------------------------------------


\begin{minipage}{\linewidth}

\question Total time taken in round robin algorithm for n process. Quantam size=q and context switch time=s  (GATE - 98)

% ----------------------------------------------------------------------------

\begin{oneparchoices}
   \choice n(s+q)
   \choice n(s-q)
   \choice n/(s+q)
   \choice n-(s*q)
\end{oneparchoices}


\end{minipage}

% ----------------------------------------------------------------------------

\begin{minipage}{\linewidth}

  \question Which scheduling algorithm provides maximum throughput. (GATE -2001 )

  \begin{oneparchoices}
    \choice Round Robin
    \choice SJF
    \choice FCFS
    \choice Priority based
  \end{oneparchoices}

\end{minipage}

% ----------------------------------------------------------------------------


\begin{minipage}{\linewidth}

  \question Which is non primitive. (GATE - 02)

  \begin{choices}
    \choice Round Robin
    \choice FCFS
    \choice Multi-level queue scheduling
    \choice Multi-level queue scheduling with feedback
  \end{choices}

\end{minipage}

% ----------------------------------------------------------------------------


\begin{minipage}{\linewidth}

  \question No of context switching in SRTF. bursts=[10,20,30] arrival=[0,2,6] (GATE - 2006)

  \begin{oneparchoices}
    \choice 1
    \choice 2
    \choice 3
    \choice 4
  \end{oneparchoices}

\end{minipage}

% ----------------------------------------------------------------------------


\begin{minipage}{\linewidth}

  \question Match the following. (GATE - 2007) \newline
   P). Gang Scheduling  Q). Rate Monotonic  R). Fair share Scheduling \newline
   1). Guranteed Scheduling 2). Real-time Scheduling 3). Thread Scheduling
  \begin{choices}
    \choice P-3, Q-2, R-1
    \choice P-1, Q-2, R-3
    \choice P-2, Q-3, R-1
    \choice P-1, Q-3, R-2
  \end{choices}


\end{minipage}

% ----------------------------------------------------------------------------

\begin{minipage}{\linewidth}

  \question Choose correct options (GATE-2010)

   \begin{enumerate}
      \item[I] SRTF causes starvation.
      \item[II] Premptive scheduling may cause starvation.
      \item[III] Round robin is bettre than FCFS in response time.
   \end{enumerate}

  \begin{choices}
    \choice I only
    \choice I, III only
    \choice II, III only
    \choice I, II, III
  \end{choices}


\end{minipage}

% ----------------------------------------------------------------------------


\begin{minipage}{\linewidth}

  \question  Given that priority is propotional to waiting time. After every T seconds priority is re-valuated.
             All process arrive at time zero with zero priority. (GATE - 2013)

  \begin{choices}
    \choice This algorithm is equivalant to FCFS.
    \choice This algorithm is equivalant to round robin.
    \choice This algorithm is equivalant to SJF.
    \choice This algorithm is equivalant to SRTF.
  \end{choices}


\end{minipage}

% ----------------------------------------------------------------------------


\begin{minipage}{\linewidth}

  \question  CPU-bound processes arrive at same time with un-equal bust.
            Which scheduling algorithm will minimize average waiting time. (GATE - 2016\_set\_1)

  \begin{choices}
    \choice SRTF
    \choice Largest Job First (opposite of SJF).
    \choice Iniform random
    \choice Round robin
  \end{choices}

\end{minipage}

% ----------------------------------------------------------------------------


\begin{minipage}{\linewidth}


  \question Highest response ratio next favours \fillin[shorter burst]  jobs, but it also limits the
            waiting time of \fillin[Long burst] jobs. (GATE - 1990)

\end{minipage}

% ----------------------------------------------------------------------------


\begin{minipage}{\linewidth}

  \question \fillin[.........] is the average waiting time for SRTF. (GATE - 2017\_set\_1) \newline
            [P1, P2, P3, P4]
            Arrival-[0,  3,  5,  6 ]
            Bursts-[7,  3,  5,  2 ]

\end{minipage}

% ----------------------------------------------------------------------------


\begin{minipage}{\linewidth}

  \question Jobs[p, q, r, s, t] bursts[4,1,8,1,2]. Completion time of P. Round robin scheduling with time slice of 1.
            Single process system. (GATE - 1993, 96)

  \begin{choices}
    \choice 4
    \choice 10
    \choice 11
    \choice 12
  \end{choices}


\end{minipage}

% ----------------------------------------------------------------------------


\begin{minipage}{\linewidth}

  \question  Choose correct sequence and cpu idle time for non preemptive scheduling.(GATE - 1995)
             \newline job-[1,2,3] Bursts-[9,5,1] Arrival-[0, 0.6, 1]
  \begin{choices}
    \choice {3,2,1}, 1
    \choice {2,1,3}, 0
    \choice {3,2,1}, 0
    \choice {1,2,3}, 5
  \end{choices}

\end{minipage}

% ----------------------------------------------------------------------------


\begin{minipage}{\linewidth}

  \question  Burst-[6,3,5, x]. Execution order for minimum average response time. (GATE - 1998)


\end{minipage}


% ----------------------------------------------------------------------------

\begin{minipage}{\linewidth}

  \question  A uni-processor computer system only has 2 processes. Both alternating 10ms CPU and 90ms IO bursts.
             Both arrive at same time. I/O of both process can proceed in parallel. For least CPU utilization. (GATE-2003 )

  \begin{choices}
    \choice FCSC
    \choice SRTF
    \choice priority scheduling with different priorities to both process.
    \choice Round robin scheduling.
  \end{choices}


\end{minipage}

% ----------------------------------------------------------------------------


\begin{minipage}{\linewidth}

  \question  Jobs-[p1, p2, p3, p4] Bursts-[5,3,3,1] Arrival-[0,1,2,4]. Average turnaroud time for SRTF. (GATE- 2004)

  \begin{oneparchoices}
    \choice 5.5
    \choice 5.75
    \choice 6
    \choice 6.25
  \end{oneparchoices}

\end{minipage}

% ----------------------------------------------------------------------------


\begin{comment}

\begin{minipage}{\linewidth}

  \question  (GATE- )

  \begin{choices}
    \choice
    \choice
    \choice
    \choice
  \end{choices}

\end{minipage}

  %% oneparchoices

\end{comment}
