\centerline{\textbf{ \LARGE Threads}}

\setcounter{question}{0}

  \question Choose the correct options. (GATE - 2004 )

  \begin{choices}
    \choice Context switching is faster in kernel threads.
    \choice System call blocks all user threads.
    \choice Kernel threads can be scheduled independently.
    \choice User threads are transparent to kernel.
  \end{choices}

  \question Which is false. (GATE -  2007)

  \begin{choices}
    \choice Kernel threads have more context switch time.
    \choice User threads need no hardware support.
    \choice Related kernal threads can be scheduled on different processors.
    \choice Blocking one kernal threads block all related threads.
  \end{choices}

  \question  Choose the correct option (GATE - 2011)

  \begin{choices}
    \choice For each thread, OS maintains only CPU register state.
    \choice For each thread, OS does not maintains  stack.
    \choice For each thread, OS does not maintains  virtual memory state.
    \choice For each thread, OS maintains only scheduling and counting information.
  \end{choices}

  \question  Choose the false option. (GATE - 2014\_set\_1)

  \begin{choices}
    \choice User level threads are not scheduled by kernel.
    \choice Blocking one user thread will block all threads of the process.
    \choice User threads have less context switching compared to kernel threds.
    \choice Kernel threads can not share the code segment.
  \end{choices}


\begin{comment}

  \question  (GATE - )

  \begin{choices}
    \choice
    \choice
    \choice
    \choice
  \end{choices}

  %% oneparchoices

\end{comment}
