
\centerline{\textbf{ \LARGE Micro Programming, Micro instructions, RISC, CISC}}


\begin{questyle}
  \question  A micro instruction into be designed to specify \\ a). none or one of the three micro
             operations of one kind and \\b). none or upto six micro operations of another kind.
             The minimum number of bits in the micro-instruction is  (GATE-1997)

  \begin{oneparchoices}
    \choice         9
    \choice         5
    \CorrectChoice  8
    \choice         None
  \end{oneparchoices}
  \\ Hint : Micro-instruction specifies 7 micro-operations. (M0, M1, M2, M3, M4, M5, M6)
  \\ Hint : M0 has 3 types.
  \\ Hint : 2 bits : Only one from (M01, M02, M03, none)
  \\ Hint : 6 bits : Any combination from (M1, M2, M3, M4, M5, M6)

    \begin{myTableStyle} \begin{tabular}{ |m{1cm}|m{0.2cm}|m{0.2cm}|m{0.2cm}|m{0.2cm}|m{0.2cm}|m{0.2cm}|m{0.2cm}| } \hline
                & M0 & M1 & M2 & M3 & M4 & M5 & M6 \\ \hline
        Options & 4  & 2  & 2  & 2  & 2  & 2  & 2 \\ \hline
        Bits    & 2  & 1  & 1  & 1  & 1  & 1  & 1 \\ \hline
    \end{tabular} \end{myTableStyle} \vspace{0.08in}
\end{questyle}

\begin{questyle}
  \question  Horizontal microprogramming :  (GATE-2002)

  \begin{choices}
    \choice         does not require use of signal decoders
    \choice         results in larger sized microinstructions than vertical microprogramming
    \choice         uses one bit for each control signal
    \CorrectChoice  all of the above.
  \end{choices}
\end{questyle}

\begin{questyle}
  \question  Arrange the following configurations for CPU in decreasing order of operating speeds.  (GATE-1999)

  \begin{choices}
    \choice         Hardwired control, Vertical microprogramming, Horizontal microprogramming.
    \CorrectChoice  Hardwired control, Horizontal microprogramming, Vertical microprogramming.
    \choice         Horizontal microprogramming, Vertical microprogramming, Hardwired control.
    \choice         Vertical microprogramming, Horizontal microprogramming, Hardwired control.
  \end{choices}
\end{questyle}


\begin{questyle}
  \question  The main difference(s) between a CISC and a RISC processor. RISC typically:  (GATE-1999)

    \begin{multicols}{2}
        \item[I] has fewer instructions
        \item[II] has fewer addressing modes
        \item[III] has more registers
        \item[IV] is easier to implement using hardwired control logic
    \end{multicols}

  \begin{oneparchoices}
    \choice         Only I and II
    \choice         Only II and III
    \choice         Only I and IV
    \CorrectChoice  I, II, III, IV
  \end{oneparchoices}
\end{questyle}

\begin{comment}

\begin{questyle}
  \question  zzz  (GATE-zzz)

  \begin{choices}
    \choice         zzz
    \choice         zzz
    \choice         zzz
    \choice         zzz
\CorrectChoice
  \end{choices}
\end{questyle}

\begin{questyle}
  \question  zzz  (GATE-zzz)

  \begin{choices}
    \choice         zzz
    \choice         zzz
    \choice         zzz
    \choice         zzz
\CorrectChoice
  \end{choices}
\end{questyle}

\end{comment}




